---
title: "Hvor grønt snakker politikere *egentlig*?"
author: "Esben Kran"
date: "June 19, 2020"
output: rmarkdown::github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "README_figs/README-"
)
```

# Politician climate analysis

```{r}
library(pacman);p_load(tidyverse, circlize, dplyr, tidytext, topicmodels, tm, plotly, tidyr, kableExtra, knitr, ggrepel, gridExtra, formattable)

```

## Theme setup
```{r}
p_load(showtext)
windows()
font_add("Euclid Flex", "C:/Users/esben/AppData/Local/Microsoft/Windows/Fonts/EuclidFlex-Regular.otf")
font_add("Euclid Flex Bold", "C:/Users/esben/AppData/Local/Microsoft/Windows/Fonts/EuclidFlex-Bold.otf")
showtext_auto()

theme_dgsb_light = 
  theme_minimal() +
  theme(
    text = element_text(family = "Euclid Flex"),
    plot.margin = unit(rep(1, 4), "cm"),
    plot.title = element_text(size = 18, 
                              family = "Euclid Flex Bold",
                              color = "#22292F",
                              face = "bold",
                              margin = margin(b = 7)),
    plot.subtitle = element_text(size = 12, 
                                 margin = margin(b = 15)),
    plot.caption = element_text(size = 11,
                                margin = margin(t = 10),
                                color = "#606F7B"),
    panel.grid.major = element_line(color = "#DAE1E7"),
    panel.background = element_blank(),
    axis.text = element_text(size = 11, color = "#22292F"),
    axis.text.x = element_text(margin = margin(t = 5)),
    axis.text.y = element_text(margin = margin(r = -10)),
    axis.title = element_text (size = 12),
    axis.line = element_blank(), #element_line(color = "#3D4852")
    axis.title.y = element_text(margin = margin(r = 5),
                                hjust = 0.5),
    axis.title.x = element_text(margin = margin(t = 5),
                                hjust = 0.5))
```

## Reading data

```{r}
df <- rbind(
  read_csv("mf_all_tweets_20200402.csv"),
  read_csv("mf_all_tweets_20200406.csv")) %>%
  cbind(
    rbind(
      read_csv("mf_all_tweets_20200402_sentiment.csv"),
      read_csv("mf_all_tweets_20200406_sentiment.csv")
    )
  )

df <- df[,-10]
keywords <- c("klima", "klimaet", "dkgreen", "co2", "climate", "dkklima", "klima", "climatechange", "klimaforandringer", "klimaforandringerne", "grøn omstilling", "green", "grøn", "grønne", "klima", "climatechange", "dkgreen")
```

## Folketingspolitikere med mængden af tweets i vores datasæt

```{r Tweet table, echo=FALSE}
screen_name_100 <- df %>%
  group_by(screen_name) %>%
  mutate(tweet_count = n()) %>%
  select(screen_name, tweet_count) %>%
  arrange(desc(tweet_count)) %>%
  unique %>%
  filter(tweet_count > 100)

df <- df %>% 
  filter(screen_name %in% screen_name_100$screen_name)

```

## Document-term matrix

```{r}
# Removes all but the characters inside the parantheses
removeSpecialChars <- function(x) gsub("[^a-zA-Z0-9æøåÆØÅ]", " ", x)

df$text <- sapply(df$text, removeSpecialChars) %>%
  tolower

# Pretty long processing time
df_fil <- df %>%
  unnest_tokens(word, text) %>%
  anti_join(data.frame(word = stopwords(kind = "da"))) %>%
  distinct()

# Document tern matrix for the happy LDA
dtm <- df_fil %>%
  count(tweet_id, word, sort = T) %>%
  ungroup() %>%
  cast_dtm(tweet_id, word, n)

```
## LDA (WARNING: Long processing time)
```{r LDA topic modelling}
k <- 20
seed = 1357
lda <- LDA(dtm, k = k, method = "GIBBS", control = list(seed = seed))
```

## Web scrape the party memberships
```{r Scraping Folketingets website for party membership}
p_load(rvest)
url <- "https://www.ft.dk/Kontakt/Telefonbog?level1=MEDLEM&pageSize=200&totalNumberOfRecords=186"
webpage <- read_html(url)
fname <- html_nodes(webpage, ".column-documents:nth-child(2)") %>%
  html_text %>%
  removeSpecialChars %>%
  str_trim
lname <- html_nodes(webpage, ".column-documents:nth-child(3)") %>%
  html_text %>%
  removeSpecialChars %>%
  str_trim
party <- html_nodes(webpage, ".column-documents:nth-child(4)") %>%
  html_text %>%
  removeSpecialChars %>%
  str_trim %>%
  str_replace("Medlem af Folketinget ", "") %>%
  str_trim %>% 
  substr(1, 2) %>%
  str_trim

party_members <- tibble(fname, lname, party) %>%
  mutate(name = paste(fname, lname))
```

## Combine based on name and add membership
```{r Combine name and party}
polit <- read_csv("folketings_politikere.csv")
polit <- inner_join(polit, party_members) %>%
  group_by(party) %>%
  arrange(party, name)

```

## Correlating party and topics
```{r Party and topics}
df <- inner_join(df, polit[,c("party","screen_name", "name")], by = "screen_name")

df$document <- as.character(df$tweet_id)

name_topic <- tidy(lda, matrix = "gamma") %>%
  inner_join(df, by = "document") %>%
  select(name, topic, gamma) %>%
  group_by(name, topic) %>%
  mutate(mean = mean(gamma)) %>%
  select(-gamma) %>%
  distinct()

party_topic <- tidy(lda, matrix = "gamma") %>%
  inner_join(df, by = "document") %>%
  select(party, topic, gamma) %>%
  group_by(party, topic) %>%
  mutate(mean = mean(gamma)) %>%
  select(-gamma) %>%
  distinct()

name_topic$topic = paste("Topic", name_topic$topic, sep = " ")
party_topic$topic = paste("Topic", party_topic$topic, sep = " ")

```

## Check topic content
```{r}
n_docs = 5
topics_tidy <- tidy(lda, matrix = "gamma")
top_documents <- topics_tidy %>%
  group_by(topic) %>%
  arrange(topic, desc(gamma)) %>%
  slice(seq_len(n_docs)) %>%
  arrange(topic, gamma) %>%
  mutate(row = row_number()) %>%
  ungroup() %>%
  #re-label topics
  mutate(topic = paste("Topic", topic, sep = " "))

top_sources <- top_documents %>%
  #join back to the tidy form to get the source field
  inner_join(df) %>%
  select(document, name, topic) %>%
  distinct() %>%
  group_by(topic) %>%
  #needed by word_chart (not relevant here)
  mutate(row = row_number()) %>%
  ungroup()

top_contents <- top_documents %>%
  #join back to the tidy form to get the source field
  inner_join(df) %>%
  select(document, text, topic) %>%
  distinct() %>%
  group_by(topic) %>%
  #needed by word_chart (not relevant here)
  mutate(row = row_number()) %>%
  ungroup()

# Topic 1: greenland + English rating (??)
# Topic 2: very number heavy
# Topic 3: education + children and socially challenged
# Topic 4: German
# Topic 5: names and P.E.T. - maybe some free speech stuff?
# Topic 6: Empty
# Topic 7: skærpet + something DF + regering?
# Topic 8: English, British (2 texts)
# Topic 9: tomatoes (haha)
# Topic 10: Tax, money, equality
# Topic 11: Green electricity and restart!!
# Topic 12: Pension + spolitik's earlier pension by job
# Topic 13: Empty
# Topic 14: Events, time stamps
# Topic 15: Research
# Topic 16: #covid19
# Topic 17: Journalism, media and proof
# Topic 18: Congratulations!
# Topic 19: Sports
# Topic 20: Finanslov 

# 3 is green

top_contents[top_contents$topic == "Topic 14",]$text

```

## Plot the word clouds of each topic

```{r fig.height=10, fig.width=8}
ap_topics <- tidy(lda, matrix = "beta")

ap_top_terms <- ap_topics %>%
  group_by(topic) %>%
  top_n(100, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

library(wordcloud)
library(reshape2)

par(mfrow = c(1,2))

ap_top_terms %>%
  acast(term ~ topic, value.var = "beta", fill = 0) %>%
  comparison.cloud(
    colors = rainbow(n = 40),
    max.words = 1000,
    title.bg.colors = "transparent",
    scale = c(4,.5),
    use.r.layout = T,
    title.size = 1,
    rot.per = 0)

```

## Model influence on topic 4

```{r Klimaomtale, fig.height=4.5, fig.width=7}
party_topic <- tidy(lda, matrix = "gamma") %>%
  inner_join(df, by = "document") %>%
  select(party, topic, gamma) %>%
  group_by(party, topic) %>%
  mutate(mean = mean(gamma)) %>%
  select(-gamma) %>%
  distinct()

party_topic <- party_topic[party_topic$topic == 14,]
party_topic$topic <- "Klima"

arrange(party_topic, mean)

partycolors <- c(
  "LG" = "#000000",
  "AL" = "#00FF00",
  "RV" =  "#E5007D",
  "SF" =  "#C4161C",
  "S" =  "#C8032C",
  "V" = "#002883",
  "EL" = "#BA2647",
  "KF" = "#00583C",
  "LA" = "#12213F",
  "NB" = "#888888",
  "DF" = "#EE0000",
  "IA" = "#AB2328"
)

party_topic$mean <- party_topic$mean * 100
party_topic <- arrange(party_topic, desc(mean))
party_topic$party <- as.factor(party_topic$party)
partycolors <- partycolors

ggplot(party_topic) +
  aes(x = reorder(party,mean), y = mean) +
  theme_minimal() +
  geom_bar(stat = "identity", fill = partycolors, color = "black", width = 1) +
  theme(legend.position = "none") +
  labs(x = "", y = "Klimaomtale", 
       title = "Klimaomtale fra de forskellige partier på Twitter",
       subtitle = "Udregnet med gennemsnittet af deres medlemmers klima-tweets.") +
  ylim(0,10) +
  coord_flip() +
  theme_dgsb_light +
  theme(panel.grid.major = element_blank())

```

## Map top sources
```{r fig.height=6, fig.width=7}
member_topic <- name_topic[name_topic$topic == "Topic 14",] %>%
  left_join(party_members, by = "name") %>%
  select(name, mean, party, fname, lname) %>%
  group_by(party) %>%
  mutate(mean = mean * 100) %>%
  arrange(desc(mean))

ggplot(member_topic[1:20,]) +
  aes(x = reorder(lname, mean), y = mean, label = party, fill = party) +
  theme_minimal() +
  geom_text(nudge_y = 0.35)  + 
  scale_x_discrete(limits = rev(levels(df$party))) +
  scale_fill_manual(
    values = partycolors,
    limits = names(partycolors)
  ) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  labs(x = "", y = "Klimaomtale", 
       title = "Politikere med højest score",
       subtitle = "Baseret på hvor meget, de snakker om klima.") +
  ylim(0,10) +
  coord_flip() +
  theme_dgsb_light +
  theme(legend.position = "none") +
  theme(panel.grid.major = element_blank())


```

## Analysing word freq

```{r Word freq}
# Isolating mr. Jørgensen's topic dependency
name_topic[name_topic$name == "Dan Jørgensen" & name_topic$topic == 14,]$mean * 100
mean(name_topic[name_topic$topic == 14,]$mean) * 100

# Defining a w/o function
log_match <- function(x, y) base::match(x, y, nomatch = 0) > 0

# Looking at mr. Jørgensen's word use frequency
word_freq <- df_fil %>%
  filter(screen_name == "DanJoergensen") %>%
  select(word) %>%
  table() %>%
  sort(decreasing = T)

# Creating such a table for every politician
df_fil_names <- inner_join(df_fil, polit[,c("screen_name", "name", "party")], by = "screen_name")

word_freq_all <- df_fil_names %>%
  select(name, word, party) %>%
  group_by(party, name) %>%
  nest %>%
  as_tibble

# Getting word frequency
word_freq_all$data <- 
  sapply(word_freq_all$data, function(x) {
    select(x, word) %>%
      table %>%
      sort(decreasing = T)
  })

# Getting sum
word_freq_all$sum <- 
  sapply(word_freq_all$data, function(x) sum(x))

# Logging percentage = keywords
word_freq_all <- word_freq_all %>%
  mutate(data = sapply(data, function(x) x / sum(word_freq_all$sum)))

# Sum of word frequency in keywords divided by total word frequencies
word_freq_all <- 
  word_freq_all %>%
  mutate(percentage =
           sapply(data,
                  function(x)
                    sum(x[names(x) %in% keywords]) / sum(x))) %>%
  arrange(desc(percentage))

```

## Plotting results from keyword frequency levels
```{r Plot word freq,fig.height=6, fig.width=7}

ggplot(word_freq_all[1:20,]) +
  aes(x = reorder(name, percentage), y = percentage, label = party, fill = party) +
  theme_minimal() +
  geom_text(nudge_y = 0.0008)  + 
  scale_x_discrete(limits = rev(levels(word_freq_all$party))) +
  scale_fill_manual(
    values = partycolors,
    limits = names(partycolors)
  ) +
  #scale_y_continuous(labels = paste0(y, "%")) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  labs(x = "", y = "Klimaomtale", 
       title = "Politikere med højest score",
       subtitle = "Baseret på frekvensen, de bruger ord om klimaet.") +
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  theme_dgsb_light +
  theme(legend.position = "none") +
  theme(panel.grid.major = element_blank())

```
## Plotting high scorer for each word

```{r}

```

## Analysing sentiment score in climate tweets
```{r}
# Classifies specific tweet as climate related
df$climate <- sapply(df$text, function(x) any(sapply(keywords, grepl, x)))

member_sentiment <- df %>%
  filter(climate == T) %>%
  group_by(name) %>%
  summarise(sentiment = mean(sentiment),
            chars = length(text))

```

# Combining the scores
```{r}
# Map percentage between 0-10
word_freq_all$score1 <- 
  (word_freq_all$percentage-min(word_freq_all$percentage))/
  (max(word_freq_all$percentage)-min(word_freq_all$percentage)) * 10

# Setup score from topics
member_topic$score2 <- 
  (member_topic$mean-min(member_topic$mean))/
  (max(member_topic$mean)-min(member_topic$mean)) * 10

# Map sentiment scores into 0-10
member_sentiment$score3 <-
  (member_sentiment$sentiment - min(member_sentiment$sentiment)) /
  (max(member_sentiment$sentiment) - min(member_sentiment$sentiment)) *  10

# member_topic        # Topic 11 member scores in 0-10 scale (6.74 is best, Mai Villadsen)
# member_sentiment    # The mean absolute sentiment score of tweets (mapped between 0-10)
# word_freq_all       # The percentage of climate words used in tweets (max = 1.94%, multiply by 500 to get 0-10)

# Get average of the different scores
member_final <- inner_join(member_topic, word_freq_all) %>% 
  inner_join(member_sentiment) %>%
  select(name, party, score1, score2, score3) %>% 
  mutate(score = (score1 + score2 + score3)/3) %>% 
  arrange(desc(score))

party_final <- member_final %>%
  group_by(party) %>%
  mutate(party_score = mean(score)) %>%
  select(party, party_score) %>%
  distinct %>%
  arrange(desc(party_score)) %>%
  filter(!(party %in% c("LG", "AL", "LA", "IA", "NB")))
```

## Plotting the final model
```{r fig.height=18, fig.width=8}
ggplot(member_final) +
  aes(x = reorder(name, score), y = score, label = party, fill = party) +
  theme_minimal() +
  geom_text(nudge_y = 0.5)  + 
  scale_x_discrete(limits = rev(levels(member_final$party))) +
  scale_fill_manual(
    values = partycolors,
    limits = names(partycolors)
  ) +
  #scale_y_continuous(labels = paste0(y, "%")) +
  geom_bar(stat = "identity", width = 1, color = "black") +
  labs(x = "", y = "Klimaomtale", 
       title = "Politikeres grønne Twitter-point",
       subtitle = "Udregnet ud fra deres tweets' frekvens af klimaord, hvor meget \nde handler om klima, og hvor positivt de snakker om klima.") +
  coord_flip() +
  ylim(0,10) +
  theme_dgsb_light +
  theme(legend.position = "none") +
  theme(panel.grid.major = element_blank())
```

## Plotting final party model
```{r fig.height=3.5, fig.width=8}
colnames(party_final) <- c("party", "score")
ggplot(party_final) +
  aes(x = reorder(party,score), y = score, fill = party) +
  theme_minimal() +
  scale_x_discrete(limits = rev(levels(party_final$party))) +
  scale_fill_manual(
    values = partycolors,
    limits = names(partycolors)
  ) +
  geom_bar(stat = "identity", color = "black", width = 1) +
  theme(legend.position = "none") +
  labs(x = "", y = "Klimaomtale", 
       title = "Partiers grønne Twitter-point",
       subtitle = "Udregnet ud fra medlemmernes tweets' frekvens af klimaord, hvor \nmeget de handler om klima, og hvor positivt de snakker om klima.") +
  ylim(0,10) +
  coord_flip() +
  theme_dgsb_light +
  theme(panel.grid.major = element_blank()) +
  theme(legend.position = "none")

```

